On Verification Patterns for Low-Level Systems via Modal Abstractions

### 2025-09-12 paper.tex
+

In addition, the modal definitions themselves may represent ownership of resources in a substructural setting~\cite{restall1993modalities,dovsen1992modal,kamide2002kripke}. 
This allows modalities to simultaneously represent ownership of certain resources used for interpreting the modality itself, as well as whatever resource ownership is implied by the modal argument.
\subsection{Decomposing a System into its Constituents \emph{Contingently}}
\label{sec:definitions}
\begin{table*}[t]\small
\centering
\caption{Modal Decomposition of Program-Logics.}
\label{table:decomposition}
 %$\{\Diamond (P) \}$ write  $\{ P\}_{n}$
%$\{\overset{ICut^{n}}{\hookrightarrow} (P) \}$ return $\{ P\}_{n} $
\begin{tabular}{@{}lcccp{4cm}@{}}
  \toprule
{ Modality}& { Context} & { Elements}  &  { Nominalization} & { Context Steps} \\ \midrule
 Post-Crash~\cite{tejthesis,perennialgit,tejperennial19} &  $\Diamond \; P $  &  $  \ell \mapsto_{n}^{\overline{\gamma}} v $ &  Strong &   Crash Recovery    \\ 
%GC-Modality &      & \multicolumn{2}{c}{\multirow{2}{*}{Because why not}} & 8                                   & & ~\cite{}\\
 NextGen~\cite{larsnextgen25} &   $\overset{t}{\hookrightarrow} \; P$  &  Own (t(a))  &  Strong &  Determined Based on the Model$^{*}$   \\
 StackRegion$^{*}$  ~\cite{larsnextgen25} &  $\overset{ICut^{n}}{\hookrightarrow} \; P$      &  $\fbox{n} \; \ell \mapsto v$                                 &  Strong &  Alloc and Return to/from stack\\
 Memory-Fence~\cite{fsl,fsl++,derekrustbelt20} &  $\triangle_{\pi}$ and $\triangledown_{\pi}$      &  $\ell \mapsto v$                                 &  Weak &  Fence Acquire and Release  \\
 Address Space~\cite{kuru2025modalabstractionsvirtualizingmemory} &  [r]P     &   $\ell \mapsto v$ &  Weak                         &  Address Space Switch  \\ 
 Ref-Count~\cite{amalreal2024}& @$_{\ell}$ P    &  $\ell_1 \mapsto v$ &  Weak  &  Allocating, Dropping and Sharing a Reference \\ \bottomrule
\end{tabular}

>>>>

In addition, the modal definitions themselves may represent ownership of resources in a substructural setting~\cite{restall1993modalities,dovsen1992modal,kamide2002kripke}. 
This allows modalities to simultaneously represent ownership of certain resources used for interpreting the modality itself, as well as whatever resource ownership is implied by the modal argument.
\subsection{Decomposing a System into its Constituents \emph{Contingently}}
\label{sec:definitions}
\begin{table*}[t]\small
\centering
\caption{Modal Decomposition of Program-Logics.}
\label{table:decomposition}
 %$\{\Diamond (P) \}$ write  $\{ P\}_{n}$
%$\{\overset{ICut^{n}}{\hookrightarrow} (P) \}$ return $\{ P\}_{n} $
\begin{tabular}{@{}lcccp{4cm}@{}}
  \toprule
{ Modality}& { Context} & { Elements}  &  { Nominalization} & { Context Steps} \\ \midrule
 Post-Crash~\cite{tejthesis,perennialgit,tejperennial19} &  $\Diamond \; P $  &  $  \ell \mapsto_{n}^{\overline{\gamma}} v $ &  Strong &   Crash Recovery    \\ 
%GC-Modality &      & \multicolumn{2}{c}{\multirow{2}{*}{Because why not}} & 8                                   & & ~\cite{}\\
 NextGen~\cite{larsnextgen25} &   $\overset{t}{\hookrightarrow} \; P$  &  Own (t(a))  &  Strong &  Determined Based on the Model$^{*}$   \\
 StackRegion$^{*}$  ~\cite{larsnextgen25} &  $\overset{ICut^{n}}{\hookrightarrow} \; P$      &  $\fbox{n} \; \ell \mapsto v$                                 &  Strong &  Alloc and Return to/from stack\\
 Memory-Fence~\cite{fsl,fsl++,derekrustbelt20} &  $\triangle_{\pi}$ and $\triangledown_{\pi}$      &  $\ell \mapsto v$                                 &  Weak &  Fence Acquire and Release  \\
 Address Space~\cite{kuru2025modalabstractionsvirtualizingmemory} &  [r]P     &   $\ell \mapsto v$ &  Weak                         &  Address Space Switch  \\ 
 Ref-Count~\cite{amalreal2024}& @$_{\ell}$ P    &  $\ell_1 \mapsto v$ &  Weak  &  Allocating, Dropping and Sharing a Reference \\
  Actor~\cite{gordon2019modal}& [A(t)]P    &  $(t,x,y)$ &  Weak  &  Send Message \\\bottomrule
\end{tabular}
